A comparative analysis of penalized linear mixed models in structured genetic data

### 2020-09-29 main.tex
3.6.5 - citing CV  maybe inadvisable for LMMs

Although cross-validation and information criterion-based methods are commonly used to select $\lambda$ values, in this context they have the potential to result in misleading comparisons across methods. Cross-validation may be inadvisable for LMMs, and in the presence of non-inedpendent samples as is the case here \anna{I know i have a citation for this somewhere FIND IT}. While information criterion methods such as BIC present another option for selecting $\lambda$, they may be unstable in high dimensions. In addition, because Lasso, PC-Lasso, and LMM-Lasso use different likelihoods, an information-criterion-based approach would not lend itself to comparable results across methods.

1000 simulations were performed for each unique combination of parameters, datatype, subpopulation structure, and environmental effect structure. \anna{somewhere else to put this that makes more sense?}

>>>>

Although cross-validation and information criterion-based methods are commonly used to select $\lambda$ values, in this context they have the potential to result in misleading comparisons across methods. Cross-validation may be inadvisable for LMMs, and in the presence of samples with underlying structure, as is the case here \citep{roberts2017cross}. While information criterion methods such as BIC present another option for selecting $\lambda$, they may be unstable in high dimensions. In addition, because Lasso, PC-Lasso, and LMM-Lasso use different likelihoods, an information-criterion-based approach would not lend itself to comparable results across methods.

1000 simulations were performed for each unique combination of parameters, datatype, subpopulation structure, and environmental effect structure.
